\textbf{COMP0086 Summative Assignment}

### 2022-11-07 main.tex
update q8 plot
add comments on protocol b plot

\title{\textbf{COMP0086 Summative Assignment}}
\author{Alexei Pisacane and Jian Shu (James) Wu \\ }
\date{Nov 16, 2022}

@@

        \item Plotting the $\ln$ of the test error for a single trial of 1000 test points versus the polynomial dimension $k = 1, . . . , 18$:
            \begin{figure}[h]
            \centering
            \includegraphics[scale=0.5]{outputs/python/q2/q2c}
            \caption{Testing Error of Polynomial Curves (1 trial)}
            \label{fig:2c}
            \end{figure}
\newpage
        \item Plotting the $\ln$ of the test error for 100 trials of 1000 test points versus the polynomial dimension $k = 1, . . . , 18$:
            \begin{figure}[h]
            \centering
            \includegraphics[scale=0.5]{outputs/python/q2/q2d}
            \caption{Testing Error of Polynomial Curves (100 trials)}
            \label{fig:2d}
            \end{figure}
    \end{enumerate}
\newpage
\item[3.] Repeating 2 (b-d) with $\sin$ basis functions:
            \begin{figure}[h]
            \centering
            \includegraphics[scale=0.5]{outputs/python/q3/q3b}
            \caption{Training Error of $\sin$ Curves}
            \label{fig:3b}
            \end{figure}
            \begin{figure}[h]
            \centering
            \includegraphics[scale=0.5]{outputs/python/q3/q3c}
            \caption{Testing Error of $\sin$ Curves (1 trial)}
            \label{fig:3c}
            \end{figure}
            \begin{figure}[h]
            \centering
            \includegraphics[scale=0.5]{outputs/python/q3/q3d}
            \caption{Testing Error of $\sin$ Curves (100 trials)}
            \label{fig:3d}
            \end{figure}
\newpage
\subsection{Filtered Boston housing and kernels}
\item[4.]
\newpage
\subsection{Kernelised ridge regression}
\item[5.]
\newpage
\section{PART II}
\subsection{$k$-Nearest Neighbors}
\item[6.]Generating a random $h$:
            \begin{figure}[h]
            \centering
            \includegraphics[scale=0.5]{outputs/python/q6/q6}
            \caption{A hypothesis $h_{S,v}$ visualised with $|S|=100$ and $v=3$}
            \label{fig:6a}
            \end{figure}
\newpage
\item[7.]
    \begin{enumerate}
        \item Producing a visualisation using Protocol A:
            \begin{figure}[h]
            \centering
            \includegraphics[scale=0.5]{outputs/python/q7/q7}
            \caption{Protocol A}
            \label{fig:7}
            \end{figure}
        \item We know that the data generating process uses $v=3$, so we would have initially expected the smallest test error to be located at the matching k-value, $k=3$.
        However, the data generating process for the training data set labels \textit{and} the testing data set labels were injected with noise, so k-values greater than 3 have a ``de-noising'' effect allowing for better performance at around $k=9$.
        As the k-value increases beyond $k=9$, this smoothing effect is too strong, causing the gradual increase in test error as the k value increases.
        For $k<9$ and in particular $k<v=3$ we see the error growing because the model has small $k$ and is able to fit to the noise injected into the data generating process, corrupting the model.
        By averaging over 100 runs, the plot is relatively smooth allowing us to make generalisations about the relationship between k-value and mean test set error.
    \end{enumerate}
\newpage
\item[8.]
    \begin{enumerate}
        \item Producing a visualisation using Protocol B:
            \begin{figure}[h]
            \centering
            \includegraphics[scale=0.5]{outputs/python/q8/q8}
            \caption{Protocol B}
            \label{fig:8}
            \end{figure}
        \item TODO
    \end{enumerate}
\newpage
\section{PART III}
\subsection{Questions}
\item[9.] \begin{enumerate}
              \item let $K_{c}(\textbf{x},\textbf{z}) = c+ \sum_{i=1}^{n}x_{i}z_{i} = c + \textbf{x}^{T}\textbf{z}$\\
        Our function $K_{c}(\cdot, \cdot)$ is psd iff:\\
        $\forall \{ u_{i} \}_{1:m} \in \mathcal{R},
         \{ \textbf{x}_{j}\}_{1:m} \in \mathcal{R}^{n}$:

>>>>

\title{\textbf{COMP0086 Summative Assignment}}
\author{Alexei Pisacane \& Jian Shu (James) Wu \\ }
\date{Nov 16, 2022}

@@

        \item Plotting the $\ln$ of the test error for a single trial of 1000 test points versus the polynomial dimension $k = 1, . . . , 18$:
            \begin{figure}[h]
            \centering
            \includegraphics[scale=0.5]{outputs/python/q2/q2c}
            \caption{Testing Error of Polynomial Curves (1 trial)}
            \label{fig:2c}
            \end{figure}
\newpage
        \item Plotting the $\ln$ of the test error for 100 trials of 1000 test points versus the polynomial dimension $k = 1, . . . , 18$:
            \begin{figure}[h]
            \centering
            \includegraphics[scale=0.5]{outputs/python/q2/q2d}
            \caption{Testing Error of Polynomial Curves (100 trials)}
            \label{fig:2d}
            \end{figure}
    \end{enumerate}
\newpage
\item[3.] Repeating 2 (b-d) with $\sin$ basis functions:
            \begin{figure}[h]
            \centering
            \includegraphics[scale=0.5]{outputs/python/q3/q3b}
            \caption{Training Error of $\sin$ Curves}
            \label{fig:3b}
            \end{figure}
            \begin{figure}[h]
            \centering
            \includegraphics[scale=0.5]{outputs/python/q3/q3c}
            \caption{Testing Error of $\sin$ Curves (1 trial)}
            \label{fig:3c}
            \end{figure}
            \begin{figure}[h]
            \centering
            \includegraphics[scale=0.5]{outputs/python/q3/q3d}
            \caption{Testing Error of $\sin$ Curves (100 trials)}
            \label{fig:3d}
            \end{figure}
\newpage
\subsection{Filtered Boston housing and kernels}
\item[4.]
\newpage
\subsection{Kernelised ridge regression}
\item[5.]
\newpage
\section{PART II}
\subsection{$k$-Nearest Neighbors}
\item[6.]Generating a random $h$:
            \begin{figure}[h]
            \centering
            \includegraphics[scale=0.5]{outputs/python/q6/q6}
            \caption{A hypothesis $h_{S,v}$ visualised with $|S|=100$ and $v=3$}
            \label{fig:6a}
            \end{figure}
\newpage
\item[7.]
    \begin{enumerate}
        \item Producing a visualisation using Protocol A:
            \begin{figure}[h]
            \centering
            \includegraphics[scale=0.5]{outputs/python/q7/q7}
            \caption{Protocol A}
            \label{fig:7}
            \end{figure}
        \item We know that the data generating process uses $v=3$, so we would have initially expected the smallest test error to be located at the matching k-value, $k=3$.
        However, the data generating process for the training data set labels \textit{and} the testing data set labels were injected with noise, so k-values greater than 3 have a ``de-noising'' effect allowing for better performance at around $k=9$.
        As the k-value increases beyond $k=9$, this smoothing effect is too strong, causing the gradual increase in test error as the k value increases.
        For $k<9$ and in particular $k<v=3$ we see the error growing because the model has small $k$ and is able to fit to the noise injected into the data generating process, corrupting the model.
        By averaging over 100 runs, the plot is relatively smooth allowing us to make generalisations about the relationship between k-value and mean test set error.
    \end{enumerate}
\newpage
\item[8.]
    \begin{enumerate}
        \item Producing a visualisation using Protocol B:
            \begin{figure}[h]
            \centering
            \includegraphics[scale=0.5]{outputs/python/q8/q8}
            \caption{Protocol B}
            \label{fig:8}
            \end{figure}
        \item k-nearest neighbours is a non-parametric model, so when queried with a test point for prediction, the number of training points within a given fixed radius of that test point increases as the number of training points increases.
        If we consider this fixed radius `sufficiently close' to make an informed prediction, the number of points within this radius will increase with more training points.
        So as the number of training points increases, the optimal k would increase to include more of the training points within this same fixed radius.
        We can see in the plot above that we see this general trend as expected, however there is considerable noise in the trend and so a smoother plot would likely requires more runs.
    \end{enumerate}
\newpage
\section{PART III}
\subsection{Questions}
\item[9.] \begin{enumerate}
              \item let $K_{c}(\textbf{x},\textbf{z}) = c+ \sum_{i=1}^{n}x_{i}z_{i} = c + \textbf{x}^{T}\textbf{z}$\\
        Our function $K_{c}(\cdot, \cdot)$ is psd iff:\\
        $\forall \{ u_{i} \}_{1:m} \in \mathcal{R},
         \{ \textbf{x}_{j}\}_{1:m} \in \mathcal{R}^{n}$:
